\cvsection{Education}
\begin{cventries}
  \cventry
    {Higher School of Economics, Faculty of Computer Science}
    {Ph.D. in computer science}
    {Moscow, Russia}
    {Jan. 2016 -- Nov. 2021}
    {
      \begin{cvitems}
        \item {Thesis: ``Optimal methods for functional connectivity estimation in magnetoencephalography.''}
      \item{Published a paper in a leading neuroscientific journal (see \cite{psiicos}})
          by proposing a method for signal leakage suppression when measuring brain areas interaction from EEG/MEG data. Programmed the algorithm and validation scripts in \textbf{MATLAB}
      % \item {GPA: 4.0}
      \end{cvitems}
    }
  % \cventry
  %   {Moscow State University, Department of Mechanics and Mathematics}
  %   {PhD in fluid mechanics, transferred to PhD program in computer science}
  %   {Moscow, Russia}
  %   {Oct. 2013 -- Jan. 2016}
  %   {
  %   }
  % \cventry
  %   {Lomonosov Moscow State University, Department of Mechanics and Mathematics}
  %   {Ph.D. in Computational Fluid Dynamics \emph{(unfinished, transferred to CS program)}}
  %   {Moscow, Russia}
  %   {Sep. 2013 --  Jan. 2016}
  %   {
  %     \begin{cvitems}
  %       \item {Thesis: ``Numerical simulations of reactive gas flows.''}
  %     \end{cvitems}
  %   }
    % {
    %   \begin{cvitems}
    %     \item {Thesis: ``Optimal methods for functional connectivity estimation in magnetoencephalography.''}
    %   \item{Published a paper in a leading neuroscientific journal (see \cite{psiicos}})
    %       by proposing a method for signal leakage suppression when measuring brain areas interaction from EEG/MEG data. Programmed the algorithm and validation scripts in \textbf{MATLAB}.
    %   % \item {GPA: 4.0}
    %   \end{cvitems}
    % }
  % \cventry
  %   {Moscow State University, Department of Mechanics and Mathematics}
  %   {PhD in fluid mechanics, transferred to PhD program in computer science}
  %   {Moscow, Russia}
  %   {Oct. 2013 -- Jan. 2016}
  %   {
  %   }
  \cventry
    {Lomonosov Moscow State University, Department of Mechanics and Mathematics}
{Specialist degree in mechanics \emph{(Masters equivalent)}}
    {Moscow, Russia}
    {Sep. 2008 -- Jun. 2013}
    {
      \begin{cvitems}
        \item{Thesis: ``Enhancement and validation of LOGOS software for simulations of the reactive fluid flows.''}
      \end{cvitems}
    }
 \cventry
    {Coursera, EdX, etc.}{Online courses}{}{}
    {
        \begin{cvitems}
            \item Algorithms \href{https://www.coursera.org/learn/algorithms-part1}{part 1}, \href{https://www.coursera.org/learn/algorithms-part2}{part 2} by Princeton University on Coursera. Assignments in \textbf{Java}
            \item \href{https://cs50.harvard.edu/x/2022/syllabus/}{CS50's itroduction to computer science} by Harvard University on EdX. Topics: \textbf{C}, \textbf{Python}, \textbf{JavaScript}, \textbf{SQL}, \textbf{HTML}, \textbf{CSS}, \textbf{Flask}
            \item \href{https://www.coursera.org/learn/machine-learning}{Machine learning} by Stanford University on Coursera. Assignments in \textbf{Octave/MATLAB}
            \item \href{https://cryptozombies.io/}{CryptoZombies} course on smart contracts in \textbf{Solidity}
        \end{cvitems}
    }
\end{cventries}
