\cvsection{Experience}

\begin{cventries}
  \cventry
    {Data scientist, contract}
    {SBDA Group}
    {Astana, Kazakhstan (remote)}
    {Sep. 2023 -- Oct. 2023}
    {
      \begin{cvitems}
          \item Developed and implemented a package for optimizing manufacturing schedule in \textbf{Python}
      \end{cvitems}
    }
  \cventry
    {Research fellow}
    {Artificial Intelligence Research Institute (AIRI)}
    {Moscow, Russia}
    {Feb. 2022 -- Apr. 2023}
    {
      \begin{cvitems}
      \item Built deep learning model for decoding speech from MEG data in \textbf{PyTorch},
          \href{https://github.com/dmalt/meg_speech_decoding}{meg\_speech\_decoding on github}
      \item Developed real-time pipeline for EEG timeseries analysis using
          \textbf{Python}
      \end{cvitems}
    }
  \cventry
    {Research fellow, Python software developer}
    {Higher School of Economics, Centre for Cognition and Decision Making}
    {Moscow, Russia}
    {Feb. 2017 -- Dec. 2021}
    {
      \begin{cvitems}
      % \item{Built a \href{https://github.com/dmalt/PSIICOS}{toolbox} for brain connectivity estimation and visualization in \textbf{MATLAB}.}
      \item{Led 4-people group developing software for real-time ML and 3D visualization of brain activity from EEG using \textbf{Python}}
            % Technologies used: \textbf{Python}, \textbf{PyQt}, \textbf{MNE-python}, \textbf{Vispy}, \textbf{Numpy}.}
      % \item{Sped up by a factor of 10 the beamformer inverse solver in \href{https://github.com/mne-tools/mne-python}{MNE-python} by modifying the algorithm for vectorized computations}
      \item{Created a pipeline for MEG data preprocessing, see \href{https://github.com/dmalt/metacognition}{metacognition}, \href{https://github.com/dmalt/MRI_metacognition}{MRI\_metacognition}} on github
      \end{cvitems}
    }
  % \cventry
  %   {Senior lecturer}
  %   {Higher School of Economics, Faculty of Computer Science}
  %   {Moscow, Russia}
  %   {Aug. 2019 -- Dec. 2021}
  %   {
  %     \begin{cvitems}
  %     \item Developed and taught a course ``\textbf{MATLAB} for data analysis'' to undergraduate students
  %     \end{cvitems}
  %   }
  \cventry
    {Visiting researcher, temporary position}
    {University of Montreal, CERNEC lab., and Moscow MEG Center}
    {Montreal, Canada, Moscow, Russia}
    % {Oct. -- Dec. 2015, May 2016 -- Dec. 2016}
    % {}
    {Feb 2015 -- Dec 2018}
    {
      \begin{cvitems}
          \item{Built a classifier for ASD patients vs. Controls with 75\% accuracy using classical ML and information geometry in \textbf{Python}}
              % \item{Supervised undergraduate student on statistial aspects of MEG data analysis}
          \item{Co-developed an open-source \textbf{Python} package for heavy neuroimaging data processing, \href{https://github.com/neuropycon}{Neuropycon}}
          \item{Published four papers in collaboration with the University of Montreal}
      \end{cvitems}
    }
  % \cventry
  %   {Visiting researcher, internship.}
  %   {University of Montreal, CERNEC lab.}
  %   {Montreal, Canada}
  %   {Oct. 2015 -- Dec. 2015}
  %   {
  %     \begin{cvitems}
  %     \item {Preprocessed MEG dataset of 90 subjects for classification using \textbf{Python} scripts.}
  %     \end{cvitems}
  %   }
  % \cventry
  %   {Junior research fellow}
  %   {Moscow State University for Pedagogics and Education, MEG Center}
  %   {Moscow, Russia}
  %   {Feb 2015 -- Dec 2018}
  %   {
  %     \begin{cvitems}
  %     \item{Published two papers in international collaboration with the University of Montreal, see \cite{Alamian2017a, Alamian2017b}}
  %     \end{cvitems}
  %   }
  \cventry
    {Research assistant, promoted to junior research fellow}
    % {SRISA RAS}
    {Scientific Research Institute of System Analysis}
    {Moscow, Russia}
    {Jun. 2011 -- Jan. 2015}
    {
      \begin{cvitems}
        \item{Tested software for simulations of flow in jet engines; implemented a droplet evaporation model in \textbf{C++}}
      \end{cvitems}
    }
\end{cventries}
